Cyclist video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda

### 2024-04-22 README.qmd

```{r}
#| echo: false
#| eval: false
# Package setup:
usethis::use_description()
usethis::use_package("sf")
usethis::use_package("stplanr")
usethis::use_package("ggplot2")
usethis::use_package("dplyr")
usethis::use_r("opsnap")

# Rbuildignore the data folder:
usethis::use_build_ignore("data")
# MIT license:
usethis::use_mit_license("Leeds Institute for Transport Studies")

# Add CI
usethis::use_github_action_check_standard()
# Add pkgdown
usethis::use_pkgdown()
# Add pkgdown action
usethis::use_github_action("pkgdown")
# Add gh pages:
usethis::use_github_pages()
```

>>>>

```{r}
#| echo: false
#| eval: false
# Package setup:
# usethis::use_description()
# usethis::use_package("sf")
# usethis::use_package("stplanr")
# usethis::use_package("ggplot2")
# usethis::use_package("dplyr")
# usethis::use_r("opsnap")
# 
# # Rbuildignore the data folder:
# usethis::use_build_ignore("data")
# # MIT license:
# usethis::use_mit_license("Leeds Institute for Transport Studies")
# 
# # Add CI
# usethis::use_github_action_check_standard()
# # Add pkgdown
# usethis::use_pkgdown()
# # Add pkgdown action
# usethis::use_github_action("pkgdown")
# # Add gh pages:
# usethis::use_github_pages()
```
